make STEM clear

### 2019-11-10 mstemc/mstemc.tex
let's call it a day

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason}
\date{\today}
\title{my workflow of creating a video}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={my workflow of creating a video},
 pdfkeywords={},
 pdfsubject={This collection of Videos and Posts describes my workflow of creating a video. Usage of some tools and methods are covered.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\section{Emacs}
\label{sec:org232de87}

@@

\subsection{program and debug}
\label{sec:orgcb33eca}

@@

\subsection{Org mode - journalize your work}
\label{sec:orga18221f}

@@

\subsection{Org mode - get things done}
\label{sec:org8f6b45e}

\subsection{Org mode - write a diary}
\label{sec:orgd48d496}

\subsection{Org mode - export your Org file}
\label{sec:org94ce70b}

\subsection{program and debug}
\label{sec:org8c82502}

\subsection{writing latex}
\label{sec:org3f6fba5}
\subsection{org-journal}
\label{sec:org9e0dc38}

@@

\subsection{ox-hugo}
\label{sec:orgeefa353}

@@

Actually, Emacs have extensions to support markdown quite well. However, using
Org, I can integrate the org file into my agenda.

\section{Hugo}
\label{sec:org4e548ff}

@@

\section{manim}
\label{sec:org74b3895}

\section{blender}
\label{sec:orge510532}
\end{document}

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason Zhang}
\date{\today}
\title{make STEM clear}
\hypersetup{
 pdfauthor={Eason Zhang},
 pdftitle={make STEM clear},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Videos}
\label{sec:org998bcda}

\section{Posts}
\label{sec:org3d17ce5}

\section{Projects}
\label{sec:orgc54445f}

\subsection{my workflow of creating a video}
\label{sec:orgf0ee6dd}
During the creation of one video, several tools are tuned to fit my workflow. In
this project several videos and posts will be created to make my workflow clear.

@@

\subsubsection{Emacs}
\label{sec:org0c108f2}

@@

\begin{enumerate}
\item program and debug
\label{sec:org1ff6423}

@@

\item Org mode - journalize your work
\label{sec:org12d2f61}

@@

\item Org mode - get things done
\label{sec:org5ad0d61}

\item Org mode - write a diary
\label{sec:org32d0506}

\item Org mode - export your Org file
\label{sec:org4d11418}

\item program and debug
\label{sec:orgeef06a2}

\item writing latex
\label{sec:org9ac1f7a}
\item org-journal
\label{sec:orga432c48}

@@

\item ox-hugo
\label{sec:orgf65906e}

@@

Actually, Emacs have extensions to support markdown quite well. However, using
Org, I can integrate the org file into my agenda.
\end{enumerate}

\subsubsection{Hugo}
\label{sec:orgc828f72}

@@

\subsubsection{manim}
\label{sec:orgea6a849}

\subsubsection{blender}
\label{sec:orge06e6d2}

\section{Courses}
\label{sec:org7e36065}
\end{document}
